Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-07-13 Supplement.tex
Remove comments

\begin{sidewaystable}[h!]\footnotesize
\centering
\begin{tabular}{lll|rrrr|rrrrr}
  \hline
Family & Mixture & Peak & $\beta^A_1$ & $\beta^A_2$ & $\beta^A_3$ & $\beta^A_4$ & $\beta^D_1$ & $\beta^D_2$ & $\beta^D_3$ & $\beta^D_4$ & $\beta^D_5$  \\
  \hline
Exponential & Non-mixture & &0.122&0.002&0.094&-1.039&-0.01&-0.056&0.118&0.249&0.164 \\
& Mixture & &0.124&0.012&0.064&-1.07&-0.068&-0.146&0.03&0.312&0.27 \\
Gamma & Non-mixture & Nonpeaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\
& & Peaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\
& Mixture & Nonpeaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\
& & Peaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\
Lognormal & Non-mixture & Nonpeaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\
& & Peaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\
& Mixture & Nonpeaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\
& & Peaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\
Weibull & Non-mixture & Nonpeaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\
& & Peaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\
& Mixture & Nonpeaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\
& & Peaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\
  \hline
\end{tabular}\\
\vspace{1.25cm}
\begin{tabular}{ll|lrrrrrrr}
  \hline
Family & Mixture & Peak & Intercept$^A$ & Intercept$^D$ & $\sigma_{A1}$ & $\sigma_{A2}$ & $\sigma_D$ & $\gamma$ & $\alpha$ \\
\hline
Exponential & Non-mixture & &0.975&-1.146&0.139&0.094&0.242& & \\
& Mixture & &1.097&-1.97&0.13&0.091&0.259&0.647& \\
Gamma & Non-mixture & Nonpeaked &1.383&-3.941&0.121&0.072&0.39& & 0.316 \\
& & Peaked &1.134&-0.746&0.121&0.072&0.39& & 3.371 \\
& Mixture & Nonpeaked &1.215&-2.7&0.121&0.079&0.332&0.79& 0.597 \\
& & Peaked &1.134&-1.21&0.121&0.079&0.332&0.65& 2.491 \\
Lognormal & Non-mixture & Nonpeaked &1.613&-2.444&0.151&0.077&0.353& & 3.287 \\
& & Peaked &1.134&-1.872&0.151&0.077&0.353& & 0.512 \\
& Mixture & Nonpeaked &1.282&-2.051&0.14&0.079&0.312&0.706& 1.467 \\
& & Peaked &1.134&-1.992&0.14&0.079&0.312&0.65& 0.618 \\
Weibull & Non-mixture & Nonpeaked &1.57&-3.137&0.131&0.074&0.383& & 0.387 \\
& & Peaked &1.134&-2.042&0.131&0.074&0.383& & 1.829 \\
& Mixture & Nonpeaked &1.294&-2.354&0.122&0.078&0.344&0.814& 0.653 \\
& & Peaked &1.134&-2.201&0.122&0.078&0.344&0.65& 1.621 \\
   \hline
\end{tabular}
\caption{\label{tbl:sim3}Table of parameter values used to generate data for simulations with covariates (Section \ref{M-sec:simfull}).  Here, $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\beta$'s are fixed effects, $\sigma$'s are random effect standard deviations, $\alpha$ is a shape parameter, and superscripts of $A$ and $D$ indicate abundance and detection parameters, respectively.}
\end{sidewaystable}
%\begin{sidewaystable}[ht]
%\centering
%\begin{tabular}{lllrrrrrrrrrrrrrrrr}
%  \hline
%Family & Mixture & Peak & Intercept$^A$ & $\beta^A_1$ & $\beta^A_2$ & $\beta^A_3$ & $\beta^A_4$ & Intercept$^D$ & $\beta^D_1$ & $\beta^D_2$ & $\beta^D_3$ & $\beta^D_4$ & $\beta^D_5$ & $\sigma_A[1]$ & $\sigma_A[2]$ & $\sigma_D$ & $\gamma$ & $\alpha$ \\ 
%  \hline
%Exponential & Non-mixture &  & 0.975 & 0.122 & 0.002 & 0.094 & -1.039 & -1.146 & -0.010 & -0.056 & 0.118 & 0.249 & 0.164 & 0.139 & 0.094 & 0.242 &  &  \\ 
%   & Mixture &  & 1.097 & 0.124 & 0.012 & 0.064 & -1.070 & -1.970 & -0.068 & -0.146 & 0.030 & 0.312 & 0.270 & 0.130 & 0.091 & 0.259 & 0.647 &  \\ 
%  Gamma & Non-mixture & Nonpeaked & 1.383 & 0.129 & -0.001 & 0.098 & -1.039 & -3.941 & 0.048 & -0.104 & -0.120 & 0.141 & 0.129 & 0.121 & 0.072 & 0.390 &  & 0.316 \\ 
%   &  & Peaked & 1.134 & 0.129 & -0.001 & 0.098 & -1.039 & -0.746 & 0.048 & -0.104 & -0.120 & 0.141 & 0.129 & 0.121 & 0.072 & 0.390 &  & 3.371 \\ 
%   & Mixture & Nonpeaked & 1.215 & 0.128 & -0.005 & 0.079 & -1.051 & -2.700 & -0.048 & -0.126 & -0.042 & 0.210 & 0.200 & 0.121 & 0.079 & 0.332 & 0.790 & 0.597 \\ 
%   &  & Peaked & 1.134 & 0.128 & -0.005 & 0.079 & -1.051 & -1.210 & -0.048 & -0.126 & -0.042 & 0.210 & 0.200 & 0.121 & 0.079 & 0.332 & 0.650 & 2.491 \\ 
%  Lognormal & Non-mixture & Nonpeaked & 1.613 & 0.126 & 0.031 & 0.096 & -1.047 & -2.444 & 0.163 & -0.099 & -0.071 & 0.310 & 0.079 & 0.151 & 0.077 & 0.353 &  & 3.287 \\ 
%   &  & Peaked & 1.134 & 0.126 & 0.031 & 0.096 & -1.047 & -1.872 & 0.163 & -0.099 & -0.071 & 0.310 & 0.079 & 0.151 & 0.077 & 0.353 &  & 0.512 \\ 
%   & Mixture & Nonpeaked & 1.282 & 0.126 & 0.017 & 0.070 & -1.068 & -2.051 & 0.006 & -0.140 & -0.038 & 0.341 & 0.191 & 0.140 & 0.079 & 0.312 & 0.706 & 1.467 \\ 
%   &  & Peaked & 1.134 & 0.126 & 0.017 & 0.070 & -1.068 & -1.992 & 0.006 & -0.140 & -0.038 & 0.341 & 0.191 & 0.140 & 0.079 & 0.312 & 0.650 & 0.618 \\ 
%  Weibull & Non-mixture & Nonpeaked & 1.570 & 0.129 & 0.011 & 0.102 & -1.040 & -3.137 & 0.101 & -0.104 & -0.127 & 0.204 & 0.086 & 0.131 & 0.074 & 0.383 &  & 0.387 \\ 
%   &  & Peaked & 1.134 & 0.129 & 0.011 & 0.102 & -1.040 & -2.042 & 0.101 & -0.104 & -0.127 & 0.204 & 0.086 & 0.131 & 0.074 & 0.383 &  & 1.829 \\ 
%   & Mixture & Nonpeaked & 1.294 & 0.129 & -0.002 & 0.081 & -1.049 & -2.354 & -0.028 & -0.122 & -0.069 & 0.204 & 0.183 & 0.122 & 0.078 & 0.344 & 0.814 & 0.653 \\ 
%   &  & Peaked & 1.134 & 0.129 & -0.002 & 0.081 & -1.049 & -2.201 & -0.028 & -0.122 & -0.069 & 0.204 & 0.183 & 0.122 & 0.078 & 0.344 & 0.650 & 1.621 \\ 
%   \hline
%\end{tabular}
%\begin{tabular}
%\end{tabular}
%\caption{\label{tbl:sim3}Table of parameter values used to generate data for simulations with covariates.  Here, $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\beta$'s are fixed effects, $\sigma$'s are random effect standard deviations, $\alpha$ is a shape parameter, and superscripts of $A$ and $D$ indicate abundance and detection parameters, respectively.}
%\end{sidewaystable}

@@

\begin{figure}[h!]\centering
%\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_correct.pdf}
%\caption{\label{pdet_cater_correct} Sim3 caterpillar plots of posterior 50\% and 95\% credible intervals for the marginal probability of detection $\pdet$.  
%Inference models come from the same family as the dataset but may differ in the presence/absence of a mixture component.  
%Each column presents one family of simulated dataset.  
%Upper plots show non-mixture datasets; lower plots show mixture datasets.  
%`X' marks the expected marginal probability of detection based on true parameter values.}
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family.pdf}
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

@@

%\small
%\section{Stan Models}\label{s:models}
%\subsection{Exponential Model}
%\lstinputlisting[breaklines]{./OVEN/Expo_model.stan}
%\subsection{Exponential Mixture Model}
%\lstinputlisting[breaklines]{./OVEN/ExpoMix.stan}
%\subsection{Gamma Model}
%\lstinputlisting[breaklines]{./OVEN/Gamma_model.stan}
%\subsection{Gamma Mixture Model}
%\lstinputlisting[breaklines]{./OVEN/GammaMix.stan}
%\subsection{Lognormal Model}
%\lstinputlisting[breaklines]{./OVEN/LogNormal_model.stan}
%\subsection{Lognormal Mixture Model}
%\lstinputlisting[breaklines]{./OVEN/LogNormalMix.stan}
%\subsection{Weibull Model}
%\lstinputlisting[breaklines]{./OVEN/Weibull_model.stan}
%\subsection{Weibull Mixture Model}
%\lstinputlisting[breaklines]{./OVEN/WeibullMix.stan}

>>>>

\begin{sidewaystable}[h!]\footnotesize
\centering
\begin{tabular}{lll|rrrr|rrrrr}
  \hline
Family & Mixture & Peak & $\beta^A_1$ & $\beta^A_2$ & $\beta^A_3$ & $\beta^A_4$ & $\beta^D_1$ & $\beta^D_2$ & $\beta^D_3$ & $\beta^D_4$ & $\beta^D_5$  \\
  \hline
Exponential & Non-mixture & &0.122&0.002&0.094&-1.039&-0.01&-0.056&0.118&0.249&0.164 \\
& Mixture & &0.124&0.012&0.064&-1.07&-0.068&-0.146&0.03&0.312&0.27 \\
Gamma & Non-mixture & Nonpeaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\
& & Peaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\
& Mixture & Nonpeaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\
& & Peaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\
Lognormal & Non-mixture & Nonpeaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\
& & Peaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\
& Mixture & Nonpeaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\
& & Peaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\
Weibull & Non-mixture & Nonpeaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\
& & Peaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\
& Mixture & Nonpeaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\
& & Peaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\
  \hline
\end{tabular}\\
\vspace{1.25cm}
\begin{tabular}{ll|lrrrrrrr}
  \hline
Family & Mixture & Peak & Intercept$^A$ & Intercept$^D$ & $\sigma_{A1}$ & $\sigma_{A2}$ & $\sigma_D$ & $\gamma$ & $\alpha$ \\
\hline
Exponential & Non-mixture & &0.975&-1.146&0.139&0.094&0.242& & \\
& Mixture & &1.097&-1.97&0.13&0.091&0.259&0.647& \\
Gamma & Non-mixture & Nonpeaked &1.383&-3.941&0.121&0.072&0.39& & 0.316 \\
& & Peaked &1.134&-0.746&0.121&0.072&0.39& & 3.371 \\
& Mixture & Nonpeaked &1.215&-2.7&0.121&0.079&0.332&0.79& 0.597 \\
& & Peaked &1.134&-1.21&0.121&0.079&0.332&0.65& 2.491 \\
Lognormal & Non-mixture & Nonpeaked &1.613&-2.444&0.151&0.077&0.353& & 3.287 \\
& & Peaked &1.134&-1.872&0.151&0.077&0.353& & 0.512 \\
& Mixture & Nonpeaked &1.282&-2.051&0.14&0.079&0.312&0.706& 1.467 \\
& & Peaked &1.134&-1.992&0.14&0.079&0.312&0.65& 0.618 \\
Weibull & Non-mixture & Nonpeaked &1.57&-3.137&0.131&0.074&0.383& & 0.387 \\
& & Peaked &1.134&-2.042&0.131&0.074&0.383& & 1.829 \\
& Mixture & Nonpeaked &1.294&-2.354&0.122&0.078&0.344&0.814& 0.653 \\
& & Peaked &1.134&-2.201&0.122&0.078&0.344&0.65& 1.621 \\
   \hline
\end{tabular}
\caption{\label{tbl:sim3}Table of parameter values used to generate data for simulations with covariates (Section \ref{M-sec:simfull}).  Here, $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\beta$'s are fixed effects, $\sigma$'s are random effect standard deviations, $\alpha$ is a shape parameter, and superscripts of $A$ and $D$ indicate abundance and detection parameters, respectively.}
\end{sidewaystable}

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family.pdf}
\caption{\label{pdet_cater_family}  Simulation results from Section \ref{M-sec:simfull}.
Caterpillar plots of posterior 50\% (orange) and 95\% (black) credible intervals for the probability of detection $\pdet$ across all surveys.
Data and models include fixed and random effects for both abundance and detection processes.
All data and inference models include mixture components.  
Each plot presents one simulated dataset.  
`X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

@@
